Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2023-06-26 LaTeX_paper/paper.tex
add definitions to proff latex paper

This section will provide a proof for the incompatibility of
the two algorithms mentioned above.
\newline \newline
The comparison algorithm deceived in section~\ref{document:my_comparator} outputs a compatibility
shore that goes from 0 to 1.\newline
But the algorithm~\ref{document:GCL} takes as input a binary value,
which means that it is necessary to apply a threshold to the input
data to convert them from float to bool.
\newline \newline
To find the optimal threshold a small 16 piece puzzle has been solved.
And the following 4 values have been measured, in function of the threshold:

@@

\centering
\includesvg[height=3.75in]{pictures/match_metrics_vs_threshold_used.svg}

>>>>

This section will provide a proof for the incompatibility of
the two algorithms mentioned above.
\newline \newline
The comparison algorithm deceived in section~\ref{document:my_comparator} outputs a compatibility
shore that goes from 0 to 1.\newline
But the algorithm~\ref{document:GCL} takes as input a binary value,
which means that it is necessary to apply a threshold to the input
data to convert them from float to bool.
\subsubsection{Input Data}
To find the optimal threshold a small 16 piece puzzle has been solved.
And the following 4 values have been measured, in function of the threshold:

@@

\begin{center}
  \includesvg[height=3.75in]{pictures/match_metrics_vs_threshold_used.svg}
\end{center}

Assuming the algorithm has to solve a 500 piece puzzle, with a limit match\% of 0.04
and a corruption rate of 0.057 (data taken from the line in red);
what would this mean in terms of accuracy of the results?

\subsubsection{Definitions}
This set of definitions are useful to better understand the next section:

\begin{itemize}
  \item \textbf{Connection:}\newline
  When two sides of two different pieces are joined they form a connection.
  A solved puzzle with \(N\) pieces, (assuming it is squared) has around \(2N\) total connections.

  \item \textbf{Possible Combinations:}\newline
  A puzzle with N pieces can be put together in many different ways,
  (even if not all of 	them actually fit together).
  The total number of possible combinations is \(N! \times 4^N\) where
  \(N!\) represent all possible way to combinate the pieces in a particular position, and
  \(4^N\) represents all possible orientations that each piece can have.
  \item \textbf{Possible Correct Combination:}\newline
  Is one of the possible combinations where all the connections are considered a match
  by the comparing algorithm.
  \item \textbf{Actual Correct Combination:}\newline
  An Actual Correct Combination is a Possible Combination that
  is also the correct solution of the original puzzle	
\end{itemize}
